---
title: "R_Presentation"
author: "CY"
date: "3/15/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library("tidyverse")
library("skimr")
```
 
From the authors of the data source:
"The aim of this study was to unravel the role of predation  in  key pests (A.  aurantii) associated with perennial citrus crops by quantifying the importance of species-specific trophic links employing, among  others, molecular  techniques.
Specifically,  i)  the  contribution  of  predation  as  a biotic  mortality  factor  of A. aurantiiwas weighted using exclusion  techniques and ii) the  relative importance of potential predators was assessed through detection of prey DNA in theirgut contents."

```{r}
predation <- readr::read_csv("L8/Predation_Data.csv")
```

```{r}
#deleted the columns of the comments the authors made in the original data with df <- df [-c(col:col')]
predation <- predation [-c(17:21)]
summary(predation)
```

What does this dataframe look like?
```{r}
predation %>% 
  skimr::skim()
```

```{r}
names(predation)
```

To understand how A. aurantii individuals' predation affect the trees they prey on, let's take a look at the tree samples used in this study! What are their orientations and what parts of them were compared? 
```{r}
predation %>%
  select(TREE, `TREE WRIENTATIWN`, `PLANT PART`, TREATMENT) %>%
  filter(TREATMENT == "Predation") %>%
  arrange(`PLANT PART`)
```

What are the mortality and parasitism rates after A. aurantii's predation?
```{r}
predation %>%
  select(TREE, TREATMENT, MORTALITY, PARASITISM) %>%
  filter(TREATMENT == "Predation") %>%
  arrange(-`MORTALITY`)
```

Let's see if there is a correlation between predation and tree mortality!
```{r}
ggplot(data=predation, mapping=aes(x=TREATMENT, y=MORTALITY, group = TREATMENT, fill = TREATMENT)) +
  geom_boxplot()
```

Are trees that became parasited more prone to die?
```{r}
predation %>%
  filter(PARASITISM > 1) %>%
  ggplot(mapping=aes(y=0.01 * PARASITISM, x= 0.01 * MORTALITY, color = `PLANT PART`)) +
  geom_point()+
  scale_colour_brewer(palette = "Dark2")+
  geom_smooth(method = lm, se = FALSE)+
  labs(title = "Parasitism Rate vs. Mortality",
       y = "Parasitism rate",
       x = "Mortality")+
  theme(plot.title = element_text(size = 14, face = "bold"),
        axis.text = element_text(size = 12),
        axis.title = element_text(size = 12))
```

Do A. aurantii smaple individuals have a favorite part of the tree to predate on?
```{r}
predation %>% 
  ggplot(aes(x=`PREDATED SCALES`, fill=`PLANT PART`))+
  geom_bar(position = position_fill(), stat = "count")+ 
  scale_y_continuous(labels = scales::percent)+
  labs(title = "Observations by tree parts that were predated",
       x = "Parts of the tree", 
       y = "Percent that were predated",
       fill= "Parts")+
  coord_flip()+
  theme(plot.title = element_text(size = 14, face = "bold"),
        axis.text = element_text(size = 12),
        axis.title = element_text(size = 12))
```

Leaf seems to be the preferred part to predate on for Aurantii individuals; let's now see if there is such a relationship between trees' orientation too!
```{r}
predation %>% 
  filter(`PREDATED SCALES` > 30 & `PREDATED SCALES` < 42) %>%
  ggplot(aes(x=`PREDATED SCALES`, fill=`GENERATION`))+
geom_bar(alpha=0.9, na.rm=T, position="dodge")+
  theme(legend.position = "right",
        axis.text.x = element_text(angle = 60, hjust=1))+
  labs(title = "Observations by generations of the predated trees",
       x = "Predation scales",
       fill= "Generation")+
theme(plot.title = element_text(size = 14, face = "bold"),
        axis.text = element_text(size = 12),
        axis.title = element_text(size = 12))
```

We now know that there is a positive correlation between mortality and A. aurantii predation, does that have anything to do with the aurantii individuals' preferred parts of the tree?
```{r}
predation %>% 
  ggplot(aes(x=`PREDATED SCALES`, y=MORTALITY, color=`PLANT PART`))+
  geom_point()+
  geom_point(shape = 18)+
  labs(title = "Observations of mortality in relation to predation, grouped by plant parts",
       x = "# Predation",
       fill= "Plant Parts")+
  theme(plot.title = element_text(size = 14, face = "bold"),
        axis.text = element_text(size = 10),
        axis.title = element_text(size = 10))

```


Now, let's see if mortality rate has a different distribution between different parts of the sample trees!
```{r}
predation %>%
  ggplot(aes(x = MORTALITY)) +
  geom_histogram() +
  facet_wrap(~`PLANT PART`)
```



```{r}
predation %>%
  filter(MORTALITY > 50) %>%
  ggplot(aes(x = MORTALITY)) +
  geom_density(fill="steelblue", alpha=0.4)+
  facet_wrap(~`PLANT PART`)
```

















