---
title: "L4H4"
author: "CY"
date: "2/4/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
life_history <- readr::read_csv("417/mammal_lifehistories_v2.csv")
```

```{r}
life_history <- 
  life_history %>% 
  dplyr::rename(
          genus        = Genus,
          wean_mass    = `wean mass`,
          max_life     = `max. life`,
          litter_size  = `litter size`,
          litters_yr   = `litters/year`
          )
```

```{r}
library("skimr")
```

```{r}
life_history %>% 
  skimr::skim()
```

```{r}
msleep %>% 
  summarize(number_nas= sum(is.na(life_history)))
```
2. There are no NAs in this dataset, which seems unlikely given the size of the data.


3. Yes. We can see from the variable typr summary above that many missing complete values were replaces with the -999. The most missing values occur at the wean mess category, which could be the result of data collection difficulty.

```{r}
life_history <- 
  life_history %>% 
  na_if(-999.0)
```
```{r}
life_history %>% 
  skimr::skim()
life_history %>%
  purrr::map_df(~ sum(is.na(.)))%>% 
  tidyr::gather(variables, num_nas) %>% 
  arrange(desc(num_nas))
```

4. Number of observations, grouped by taxonomic order.
```{r}
life_history %>%
  group_by(order) %>% 
  summarize(n())
```

5.Summary of mammal lifespan:
```{r}
life_history %>%
  mutate(lifespan=max_life/12) %>% 
  group_by(order) %>%
  summarize(min=min(lifespan, na.rm=TRUE),
            max=max(lifespan, na.rm=TRUE),
            mean=mean(lifespan, na.rm=TRUE),
            sd=sd(lifespan, na.rm=TRUE),
            total=n())
```

6. Gestation and Newborns:
```{r}
life_history %>% 
  group_by(order) %>% 
  summarize(mean_gestation=mean(gestation, na.rm=TRUE),
            mean_newborn_mass=mean(newborn, na.rm=TRUE),
            mean_wean_mass=mean(wean_mass, na.rm=TRUE),
            total=n()) %>% 
  arrange(desc(mean_gestation))
```

